Learning constraints in spreadsheets and tabular data

### 2016-12-13 Paper/ECAI/tabular.tex
updating revision letter

\bibliographystyle{plain}
{
  \bibliography{references}}
\appendix
\section{Spreadsheet Dataset Overview}
\label{appendix:dataset_overview}
\sergey{Samuel, we need an extended discussion here on how the data was obtained, I'll try a first sketch here}\\
There are three main sources for spreadsheets we have collected.
\begin{itemize}
  \item After identification of popular Excel functions (MS Office web page has an overview of popular functions), we have searched for online tutorials about these functions and collected them under the category \textbf{Tutorials}.
  \item We have collected the exercises under the category \textbf{Exercises} from the introductory Excel book \cite{excel_book} that focused on popular Excel functions.
  \item We have collected under the category \textbf{Data} publicly available economic and crime reporting data from the U.S. Bureau of Economic Analysis (BEA) and U.S. FBI Uniform Crime Reporting (UCR) Program.
\end{itemize}

>>>>

\bibliographystyle{plain}
{
  \bibliography{references}}
\appendix
\section{Spreadsheet Dataset Overview} \label{appendix:dataset_overview}
\sergey{Samuel, we need an extended discussion here on how the data was obtained, I'll try a first sketch here}\\
There are three main sources for spreadsheets we have collected.
\begin{itemize}
  \item After identification of popular Excel functions (the MS Office web page has an overview of popular functions), we have searched for online tutorials about these functions and collected them under the category \textbf{Tutorials} (a link to each webpage found and used is provided in the accompanying github repository).
  \item We have collected the exercises under the category \textbf{Exercises} from the introductory Excel book \cite{excel_book} that focused on popular Excel functions.
  \item We have collected under the category \textbf{Data} publicly available economic and crime reporting data from the U.S. Bureau of Economic Analysis (BEA) and U.S. FBI Uniform Crime Reporting (UCR) Program (the links are also provided in the accompanying github repository).
\end{itemize}
